Dominance Regions for Rank Two Cluster Algebras

### 2022-04-04 dominance_regions.tex
Pictures

\begin{figure}[h!]
  \centering
    \newcommand{\boundingrays}{
      \tikzmath{\b = 2; \c = 2.1; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
      \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -6; \ymax = 6;}
      \draw [color=lightgray, thick] (\xmin,0) -- (\xmax,0);
      \draw [color=lightgray, thick] (0,\ymin) -- (0,\ymax);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax / \b);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \c / \bcmo );
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \bcms / 2 / \b); 
      \draw [color=lightgray, thick] (0,0) -- ( - 2 * \b * \ymin / \bcps, \ymin); 
    }
  \begin{tikzpicture}[scale=.3]
    \begin{scope}[shift={(0,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (\l,\l) circle (6pt);
    \end{scope}
    \begin{scope}[shift={(13,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (\l *\b + \l, - \l)  circle (6pt);
      \draw [very thick] (\l * \b + \l, -\l) -- (\l,-\l);
    \end{scope}
    \begin{scope}[shift={(26,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (-\l, \l)  circle (6pt);
      \draw [very thick] (-\l, \l) -- (-\l,\l + \l*\c);
    \end{scope}
    \begin{scope}[shift={(39, 0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (-\l, -\l)  circle (6pt);
      \draw [very thick] (-\l, -\l) -- (-\l - \l *\b, -\l) -- (-\l - \l*\b, \l*\c + \l*\b * \c -\l) -- (-\l, \l*\c -\l) -- cycle;
    \end{scope}
    \begin{scope}[shift={(0,-13)}]
      \boundingrays;
      \tikzmath{ \l = 3; \x = \b * \l - \l / 2 / \c; \y = -\l; }
      \fill (\b * \l - \l / 2 / \c , -\l)  circle (6pt);
      \draw [very thick] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
    \end{scope}
    \begin{scope}[shift={(13,-13)}]
      \boundingrays;
      \tikzmath{ \l = 2; \x = \b * \l - \l / 2 / \c; \y = -\l - 3*\l/10;}
      \fill (\x,\y)  circle (6pt);
      \draw [very thick] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  cycle;
    \end{scope}
    \begin{scope}[shift={(26,-13)}]
      \boundingrays;
      \tikzmath{ \l = 2; \x = \l/2/\c; \y = -\l; }
      \fill (\l / 2 / \c , -\l)  circle (6pt);
      \draw [very thick] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  cycle;
    \end{scope}
    \begin{scope}[shift={(39,-13)}]
      \boundingrays;
      \tikzmath{ \l = 3; \x = \c*\l/\b/1.03; \y = -\l; }
      \fill (\x , \y)  circle (6pt);
      \draw [very thick] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  cycle;
    \end{scope}
  \end{tikzpicture}
\end{figure}

>>>>

\begin{figure}[h!]
  \centering
    \newcommand{\boundingrays}{
      \tikzmath{\b = 2; \c = 2.1; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
      \tikzmath{ \xmin = -6; \xmax = 6; \ymin = -6; \ymax = 6;}
      \draw [color=lightgray, thick] (\xmin,0) -- (\xmax,0);
      \draw [color=lightgray, thick] (0,\ymin) -- (0,\ymax);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax / \b);
      \draw [color=lightgray, thick] (0,0) -- (\xmax, -\xmax * \c / \bcmo );
      \draw [color=lightgray, thick, dashed] (0,0) -- (\xmax, -\xmax * \bcms / 2 / \b); 
      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 2 * \b * \ymin / \bcps, \ymin); 
    }
  \begin{tikzpicture}[scale=.3]
    \begin{scope}[shift={(0,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (\l,\l) circle (6pt);
    \end{scope}
    \begin{scope}[shift={(13,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (\l *\b + \l, - \l)  circle (6pt);
      \draw [very thick, join=round] (\l * \b + \l, -\l) -- (\l,-\l);
    \end{scope}
    \begin{scope}[shift={(26,0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (-\l, \l)  circle (6pt);
      \draw [very thick, join=round] (-\l, \l) -- (-\l,\l + \l*\c);
    \end{scope}
    \begin{scope}[shift={(39, 0)}]
      \boundingrays;
      \tikzmath{ \l = 1; }
      \fill (-\l, -\l)  circle (6pt);
      \draw [very thick, join=round] (-\l, -\l) -- (-\l - \l *\b, -\l) -- (-\l - \l*\b, \l*\c + \l*\b * \c -\l) -- (-\l, \l*\c -\l) -- cycle;
    \end{scope}
    \begin{scope}[shift={(0,-13)}]
      \boundingrays;
      \tikzmath{ \l = 3; \x = \b * \l - \l / 2 / \c; \y = -\l; }
      \fill (\b * \l - \l / 2 / \c , -\l)  circle (6pt);
      \draw [very thick, join=round] (\x,\y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- ( \b*\c*\x + \x + \b*\b*\c*\y,  -\c*\x - \b*\c*\y + \y) --  cycle;
    \end{scope}
    \begin{scope}[shift={(13,-13)}]
      \boundingrays;
      \tikzmath{ \l = 2; \x = \b * \l - \l / 2 / \c + 0.15; \y = -\l - 3*\l/10;}
      \fill (\x,\y)  circle (6pt);
      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dashed] (0,0);
      \draw [very thick, dashed, join=round] (0,0) --  (\x , \y);
    \end{scope}
    \begin{scope}[shift={(26,-13)}]
      \boundingrays;
      \tikzmath{ \l = 2; \x = \l/2/\c; \y = -\l; }
      \fill (\l / 2 / \c , -\l)  circle (6pt);
      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y , \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dashed] (0,0);
      \draw [very thick, dashed, join=round] (0,0) --  (\x , \y);
    \end{scope}
    \begin{scope}[shift={(39,-13)}]
      \boundingrays;
      \tikzmath{ \l = 3; \x = \c*\l/\b/1.03; \y = -\l; }
      \fill (\x , \y)  circle (6pt);
      \draw [very thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) edge[dashed] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s);
      \draw [very thick, dashed, join=round] (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
    \end{scope}
  \end{tikzpicture}
\end{figure}
